Analyzing TA Comments on Student Writing in R

### 2018-11-29 course_notes.Rmd
updates

---
title: "Course Notes"
bibliography: library.bib
biblio-style: apalike
---

@@

You can detail what you learned in the session within these pages. You can also use the Rmd markdown language and insert code chunks with `CMD/CTRL + SHIFT + I`.

# Session 1
Change

# Session 2

# Session 3

# Session 4

# Session 5

# Session 6

# Session 7

# Session 8

@@

>>>>

---
title: "Notes & Ideas"
bibliography: library.bib
biblio-style: apalike
---

@@

# Session 1 (Oct. 1, 2018)
Change

####\

# Session 2 (Oct. 22, 2018)

####\

# Session 3 (Nov. 12, 2018)

####\

# Session 4 (Dec. 3, 2018)

####\

# Session 5 (Jan. 14, 2019)

####\

# Session 6 (Feb. 4, 2019)

####\

# Session 7 (Feb. 25, 2019)

####\

# Session 8 (Mar. 18, 2019)

####\

@@

####\

### 2018-11-29 index.Rmd
updates

---
title: "Data Analysis in R: Research & Learning"
---

@@

## So It Begins

This is a general landing page for your website for your project. This is just a launching pad for our community. Feel free to customise as much as you would like.

You can use this page to give introductions about what you are doing and your aims.

The structure of the website can be changed by manipulating the `_site.yml`. Font Awesome icons are available to use. You can check those out [here](https://fontawesome.com/v4.7.0/icons/).

## General Structure

We have provided a rough template for your website
- **course_notes.Rmd** - Write your notes for the class, try some code, work some exercises and use this as a virtual notepad for the items we review. This is a great way to showcase new skills and serve as a reference when you can't quite remember how you did something

- **pre_work.Rmd** - Use this document to complete any pre-work assignments.

- **project.Rmd** - As you might have guessed, use this section to write up your project

- **library.bib** - is text file that is available for you to put citations. You can then use these citations in the other Rmd documents. Also note that if you want to cite a package and want the bibtex you can do this by using the command `citation("packagename")`.

- **footer.html** - Go ahead and put your name in there!

When you are happy with what you have written for the day, go ahead and make a website out of it by using the following command in the console `rmarkdown::render_site()`

>>>>

---
title: "Analyzing TA Comments on Student Writing in R"
---

@@

## Background
I am interested in understanding how students learn technical writing skills in biology, and how we can use data science methods to improve that process.

Our NSF-sponsored project asks if and how scripted instruction, automated support, and holistic feedback accelerates student development as writers. One of our specific aims is to see if changing the structure and focus of instructors' comments affects how students' writing develops over time. To do this, we need to extract instructor comments from student reports, classify those comments, and correlate the types of comments with student performance.

#### \   
## Prior Work
In Summer 2018, we extracted and tabulated ~11,000 TA comments from ~500 pairs (initial submissions and revised version) of short lab reports written by undergraduates in 3 different general biology lab courses collected during a single semester. Using an iteratively generated codebook, all 11,000 comments were tagged in two categories:

* __Subject__: did the comment focus mainly on Basic criteria, Technical issues, Writing quality, Logic, or Other issues
* __Structure__: was the comment mainly Copy correction, General or Specific information, Pointing to another resource, or Holistic coaching for improvement?

#### \   
Counts of the coded TA comments were sorted into a two-axis contingency table. This table provided two pieces of information:

* A snapshot of the most common types of comments TAs made, and 
* A relative estimate of where TAs are placing their greatest effort.

#### \   
## Specific Project Goals
An existing Unix-based script can extract TA comments and meta-data for each student report then assemble the data into a CSV file. Classifying TA comments by hand is impractical for routine use though; 10-12,000 score-able comments are generated EACH SEMESTER. An automated classification method is needed both for speed and consistency.

For my project I will be building an R-based text analysis workflow that:

1. **Creates a de-identified dataset.** Required data will be extracted from the master dataset and organized in an anonymized data frame where all names, comments, and confidential metadata are re-keyed to unique random identifiers.
2. **Classifies TA comments according to our existing codebook**. Initially I will be evaluating whether terms frequencies can be used to classify comments. The goal is to be able to assign instructor comments into our pre-defined Subject and Structure codes with 90% accuracy or greater 
3. **Sorts TA comments using unsupervised grouping methods**. The codebook for classifying TA comments makes prior assumptions about most relevant features. Unsupervised grouping may uncover more robust or informative classification methods.

#### \

### 2018-11-29 questions.rmd
updates

# R Code
#### I can write code for Shiny and build pages locally, but they do not build for a website. 
The build stalls here, with the error message:

>label: unnamed-chunk-1 (with options) 
>List of 1  
> $ echo: logi FALSE  
>Error in selectInput("n_breaks", label = "Number of bins:", choices = c(10,  :   
>  could not find function "selectInput"  
>Calls: <Anonymous> ... handle -> withCallingHandlers -> withVisible -> eval -> eval  
>Execution halted  
>Exited with status 1.

@@

#### Still not sure I know difference between a fork and a branch. 
Branch is an alternative version of a single file, but fork is a copy of the original repo in total. Y/N?

>>>>

# R Code
#### I cannot get numbers on CSV extracted data frames.

@@

#### Question about fork and branch. 
When I fork another repo, I get comments saying I am "#" steps ahead of it. Should I clone instead?
